---
title: "#TidyTuesday 2019-50"
author: James Wade
output: html_notebook
---

Here is my entry for [#TidyTuesday](https://github.com/rfordatascience/tidytuesday) from 2019-50: 'You can make it in R.'

# Part 1: Diseases

## Import the Data

```{r}
library(tidyverse)
library(gganimate)
library(waffle)

if(!file.exists("data/diseases.rds")) {
  d <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/diseases.csv")
  if(!dir.exists("data")) {
    dir.create("data")
  }
  write_rds(disease, "data/diseases.rds",)
} else disease <- read_rds("data/diseases.rds")

d2 <- disease %>% 
  group_by(year, state, disease) %>% 
  mutate(rate = count / population * 10000 * 52 / weeks_reporting) %>% 
  ungroup()
```

## Measles Plot with Vaccine

```{r}
jet.colors <- colorRampPalette(c("#F0FFFF", "cyan", "#007FFF", "yellow", 
                                 "#FFBF00", "orange", "red", "#7F0000"), bias = 2.25)


p_anim <- ggplot(d2 %>% filter(disease == "Measles"), aes(x = year, y = state, fill = rate)) + 
  geom_tile(color = "white", size = 0.35) +
  scale_x_continuous(expand = c(0,0)) +
  scale_fill_gradientn(colors = jet.colors(16), na.value = 'white') +
  theme_minimal() +
  transition_time(year) + shadow_mark() +
  annotate(geom = "text", x = 1963.5, y = 50.5, label = "Vaccine introduced", size = 5, hjust = 0) +
  ggtitle("Incidence of Meases (USA) \n1928-2011") +
  geom_vline(xintercept = 1963, col = "black") +
  labs(x = "Year", y = "State", fill = "Rate\n(Cases per 100,000)")

anim_save(p_anim, width = 1000, height = 600, width = 100, filename = "measles.gif")
```


```{r}
# states <- c("Alabama", "California", "Colorado", "Michigan", "New York", "Texas")
states <- c("Georgia")

p_waffle <- ggplot(d2 %>% filter(state %in% states, year %in% c(1976:1995))) +
  geom_waffle(aes(fill = disease, values = count), 
              color = "white", n_rows = 50, flip = TRUE) +
  facet_wrap(~year) +
  coord_equal() +
  ggtitle("Measles Outbreak in Geogia \n(1980-2000") +
  theme_classic()

p_line <- ggplot(d2 %>% filter(state %in% states, year %in% c(1940:2000))) +
  geom_line(aes(x = year,color = disease, y = count))

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

